A pipeline to analyse time-course gene expression data

### 2019-07-24 scripts/manuscript.Rmd
fix figure reference
ENH Moving moanin to it's own repository

library(moanin)

@@

@@

- `biocLite` is no longer the recommended way to install bioconductor. Instead `BiocManager::install(c('edge', 'NMI'))`. But this is dependent on bioconductor/R version. Also, now that docker, can you change the installation to just be simple one-liner (and `BiocManager::install` can also do non-bioc packages, and is much more reliable.)

@@

```
label: enrichment_analysis (with options) 
List of 2
 $ results: chr "hide"
 $ message: logi FALSE

Quitting from lines 1124-1138 (manuscript.Rmd) 
Error in getBM(attributes = c("ensembl_gene_id", "entrezgene"), filters = "refseq_mrna",  : 
  Invalid attribute(s): entrezgene 
Please use the function 'listAttributes' to get valid attribute names
Calls: <Anonymous> ... withCallingHandlers -> withVisible -> eval -> eval -> getBM
```

@@

We present here a workflow for such an analysis that consists of 4 main
parts (Figure \ref{fig:workflow}):

>>>>

@@

```{r}
library(devtools)
install_github("NelleV/moanin", dependencies=FALSE)

library(moanin)
```

@@

- `biocLite` is no longer the recommended way to install bioconductor. Instead
  `BiocManager::install(c("edge", "NMI"))`. But this is dependent on
  bioconductor/R version. Also, now that docker, can you change the
  installation to just be simple one-liner (and `BiocManager::install` can
  also do non-bioc packages, and is much more reliable.)

@@

@@

We present here a workflow for such an analysis that consists of 4 main
parts (Figure \ref{fig:schema}):
